Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-11-12 lloveras_2020.tex
primeros graficos

>>>>

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT results: $N_e$ (left panels) and $T_\textrm{m}$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$ ,$1.065$ $1.105\,\mrsun$, respectively. Black voxels correspond to non-reconstructed regions and thick-black curves indicate the open/closed boundaries.}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2082} but for CR-2208.}
\label{carmaps_demt_2208}
\end{center}
\end{figure}

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2082} but for AWSoM results.}
\label{carmaps_awsom_2082}
\end{center}
\end{figure}

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2208} but for AWSoM results.}
\label{carmaps_awsom_2208}
\end{center}
\end{figure}
